\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-17 ms/adult.tex
Update
Added quantile results for duration and proportion duration. Also tidied up SI a little.

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{../figs/quantile_reg_nonzero_duration_adult.pdf}
\label{fig:quantile_regression_duration}
\end{figure}

@@

@@

\clearpage
\section{Top 25 Adult Domains}

\begin{figure}[h]
	\centering
	\caption{Top 25 Adult Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
		\caption*{\footnotesize \emph{Notes:} 
			Table shows the top 25 adult sites that panelists visit in the sample period.
			Adult sites are categorized by YouGov.
			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
			Sites to the right of the vertical dashed are the top 1 percent.
		}
	\label{fig:top25_adult}
\end{figure}

\begin{figure}[h]
	\centering
	\caption{Top 25 (Non-Adult) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
		\caption*{\footnotesize \emph{Notes:} 
			Table shows the top 25 non-adult sites that panelists visit in the sample period.
			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
			Sites to the right of the vertical dashed are the top 1 percent.
		}
	\label{fig:top25_nonadult}
\end{figure}

\section{Consequence of Using Alternate Ways of Measuring Pornography}
\subsection{Keyword Classifier}
Our first classifier is based on just the domain name and domain suffix. In particular, we use a calibrated keyword classifier. The features of the model are whether any of the following keywords are present in the domain name:

@@

\section{Analysis of Visits}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits.pdf}
\label{fig:distribution_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits_by_party.pdf}
\label{fig:distribution_prop_visits}
\end{figure}

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online by Party}
\includegraphics[scale=.75]{../figs/distribution_visits_to_adultsites_by_party.pdf}
\label{fig:distribution_visits_party}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\caption{Quantile Estimates--Hours Spent on Adult Sites by Party}
\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
}
\label{fig:quantile_regression_duration}
\end{figure}

\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

\FloatBarrier
%===============================================================================
% Supplementary Descriptives for sense of landscape of porn consumption
%===============================================================================
\section{Supplementary Descriptive Figures and Tables}
\begin{figure}[ht]
	\centering
	\caption{Top 25 Adult Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 adult sites that panelists visit in the sample period.
		Adult sites are categorized by YouGov.
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent.
	}
	\label{fig:top25_adult}
\end{figure}

\begin{figure}
	\centering
	\caption{Top 25 (Non-Adult) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-adult sites that panelists visit in the sample period.
		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent.
	}
	\label{fig:top25_nonadult}
\end{figure}

@@

\FloatBarrier
%===============================================================================
% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
%===============================================================================
\section{Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography}
\subsection{Keyword Classifier}
Our first classifier is based on just the domain name and domain suffix. In particular, we use a calibrated keyword classifier. The features of the model are whether any of the following keywords are present in the domain name:

@@

\subsection{Alternative Analyses of Time Spent on Pornography}

%=====================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (with covariates) 
%=====================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
	}
	\label{fig:quantile_regression_duration_covariates}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
	}
	\label{fig:quantile_regression_prop_duration_covariates}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes panelists who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
\section{Analysis of Visits}
